\documentclass[runningheads]{llncs}
\usepackage{graphicx}

% Gets rid of font shapes not available warnings
\usepackage[utf8]{inputenc}

% uses files for each chapter
\usepackage{subfiles}
 
\usepackage{hyperref}

% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
\usepackage{color}
\renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}

\title{Corpora Evaluation and System Bias Detection in Multi-document Summarization}
\subtitle{A critical approach}

%
\titlerunning{Corpora Evaluation and System Bias Detection}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\institute{University of Bamberg, Bamberg, Germany\\
    \email{yannick-stephan.lang@stud.uni-bamberg.de}}

\author{Yannick Lang \\
    \small Study Program: B.Sc. Applied Computer Science }

\authorrunning{Y. Lang}

%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
    The abstract should briefly summarize the contents of the paper in
    150--250 words.
    
    \keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}
%
%
%

\section{Introduction}
\label{sec:introcution}
\subfile{sections/10_introduction}

\section{Introduction}
\subsection{A Subsection Sample}
Please note that the first   paragraph of a section or subsection is
not indented. The first paragraph that follows a table, figure,
equation etc. does not need an indent, either.

Subsequent paragraphs, however, are indented.\cite{Poisonin18:online}

\subsubsection{Sample Heading (Third Level)} Only two levels of
headings should be numbered. Lower level headings remain unnumbered;
they are formatted as run-in headings.

\bibliographystyle{splncs04}
\bibliography{references}
\end{document}
